Drivers of sex differences in consumption

### 2017-07-03 sex-difference/sex-difference.Rmd
fixes

```{r load_data}
year = 2011

@@

```{r}
denom = bene %>% count(sex) %>% rename(n_denom=n)
ubs = pde %>%
  select(bene_id, antibiotic) %>%
  distinct() %>%
  left_join(select(bene, bene_id, sex), by='bene_id') %>%
  count(sex, antibiotic) %>%
  ungroup() %>%
  rename(n_user=n) %>%
  left_join(denom, by='sex') %>%
  mutate(frac_using=n_user/n_denom) %>%
  select(antibiotic, sex, frac_using) %>%
  spread(sex, frac_using)
```

```{r drug_by_sex_plot}
ubs %>%
  mutate(highlight=antibiotic %in% c('azithromycin', 'ciprofloxacin', 'trimethoprim/sulfamethoxazole', 'fosfomycin', 'nitrofurantoin')) %>%
  ggplot(aes(x=male, y=female, label=antibiotic, color=highlight)) +
  scale_color_manual(values=c('black', 'red')) +
  geom_abline() +
  geom_abline(slope=1.28, col='gray') +
  geom_text() +
  geom_point() +
  xlab('claims per 1,000 male beneficiaries') +
  ylab('claims per 1,000 female beneficiaries') +
  theme_minimal() +
  coord_fixed()
```

```{r drug_by_sex_plot2}
total_plot_f = function(df, highlight=character(0)) {
  df %>%
    #mutate_at(vars(total, se), mpy) %>%
    mutate(ci=se*1.96,
           ci_low=total-ci,
           ci_high=total+ci) %>%
    select(drug, sex, total, ci_low, ci_high) %>%
    gather('key', 'value', total, ci_low, ci_high) %>%
    mutate(key=case_when(.$sex=='male' & .$key=='total' ~ 'x',
                         .$sex=='male' & .$key=='ci_low' ~ 'xmin',
                         .$sex=='male' & .$key=='ci_high' ~ 'xmax',
                         .$sex=='female' & .$key=='total' ~ 'y',
                         .$sex=='female' & .$key=='ci_low' ~ 'ymin',
                         .$sex=='female' & .$key=='ci_high' ~ 'ymax')) %>%
    select(-sex) %>%
    spread(key, value) %>%
    mutate(highlight=drug %in% highlight) %>%
    ggplot(aes(x=x, xmin=xmin, xmax=xmax, y=y, ymin=ymin, ymax=ymax, label=drug, color=highlight)) +
    geom_abline(col='gray') +
    geom_point() + geom_errorbar() + geom_errorbarh() +
    scale_color_manual(values=c('black', 'red')) +
    geom_text() +
    #geom_text(nudge_x=1, nudge_y=0.5) +
    #scale_x_continuous(breaks=c(0, 5, 10), limits=c(0, 12)) +
    #scale_y_continuous(breaks=c(0, 5, 10), limits=c(0, 14)) +
    xlab('No. rx. for men (millions)') + ylab('No. rx. for women (millions)') +
    coord_fixed() +
    theme_minimal()
}

ubs %>%
  rename(total=mean_n_claims, se=se_n_claims) %>%
  total_plot_f()
```

>>>>

```{r load_data}
year = 2014

@@

```{r compute_ubs}
denom = bene %>% count(sex) %>% rename(n_denom=n)
ubs = pde %>%
  select(bene_id, antibiotic) %>%
  distinct() %>%
  left_join(select(bene, bene_id, sex), by='bene_id') %>%
  count(sex, antibiotic) %>%
  ungroup() %>%
  rename(n_user=n) %>%
  left_join(denom, by='sex') %>%
  mutate(frac_using=n_user/n_denom) %>%
  select(antibiotic, sex, frac_using) %>%
  spread(sex, frac_using)
```

```{r drug_by_sex_plot}
ubs %>%
  mutate(highlight=antibiotic %in% c('azithromycin', 'ciprofloxacin', 'trimethoprim/sulfamethoxazole', 'fosfomycin', 'nitrofurantoin')) %>%
  ggplot(aes(x=male, y=female, label=antibiotic, color=highlight)) +
  scale_color_manual(values=c('black', 'red')) +
  geom_abline() +
  #geom_abline(slope=c(1.06, 1.109, 1.366, 1.41, 2.202), col='gray') +
  #geom_abline(slope=c(1.062406, 1.0976, 1+0.26*1.268177), col='blue') +
  geom_abline(slope=exp(3)*(1.06)) +
  # NAMCS: all adult usage 1.495, UTI: 2.164, ARC: 1.0976
  # Medicare: nabxclaims 1.24, n OP days 1.062406, arc 1.108944, uti 2.268177, copd MALE! 1.123728
  geom_text() +
  geom_point() +
  xlab('claims per 1,000 male beneficiaries') +
  ylab('claims per 1,000 female beneficiaries') +
  theme_minimal() +
  coord_fixed()
```

```{r}
dx %>%
  count(bene_id, diagnosis_type) %>%
  ungroup() %>%
  right_join(bene, by='bene_id') %>%
  group_by(sex) %>%
  summarize(mn=mean(n), n_bene=n())
```

```{r drug_by_sex_plot2, eval=FALSE}
total_plot_f = function(df, highlight=character(0)) {
  df %>%
    #mutate_at(vars(total, se), mpy) %>%
    mutate(ci=se*1.96,
           ci_low=total-ci,
           ci_high=total+ci) %>%
    select(drug, sex, total, ci_low, ci_high) %>%
    gather('key', 'value', total, ci_low, ci_high) %>%
    mutate(key=case_when(.$sex=='male' & .$key=='total' ~ 'x',
                         .$sex=='male' & .$key=='ci_low' ~ 'xmin',
                         .$sex=='male' & .$key=='ci_high' ~ 'xmax',
                         .$sex=='female' & .$key=='total' ~ 'y',
                         .$sex=='female' & .$key=='ci_low' ~ 'ymin',
                         .$sex=='female' & .$key=='ci_high' ~ 'ymax')) %>%
    select(-sex) %>%
    spread(key, value) %>%
    mutate(highlight=drug %in% highlight) %>%
    ggplot(aes(x=x, xmin=xmin, xmax=xmax, y=y, ymin=ymin, ymax=ymax, label=drug, color=highlight)) +
    geom_abline(col='gray') +
    geom_point() + geom_errorbar() + geom_errorbarh() +
    scale_color_manual(values=c('black', 'red')) +
    geom_text() +
    #geom_text(nudge_x=1, nudge_y=0.5) +
    #scale_x_continuous(breaks=c(0, 5, 10), limits=c(0, 12)) +
    #scale_y_continuous(breaks=c(0, 5, 10), limits=c(0, 14)) +
    xlab('No. rx. for men (millions)') + ylab('No. rx. for women (millions)') +
    coord_fixed() +
    theme_minimal()
}

ubs %>%
  gather('sex', 'total', female, male) %>%
  left_join(bene %>% count(sex) %>% rename(n_bene=n), by='sex') %>%
  mutate(se=total/sqrt(n_bene)) %>%
  rename(drug=antibiotic) %>%
  total_plot_f() +
  geom_abline(slope=c(1.06, 1.306122), col='gray')
```
